\section{Experience}

\resumeSubHeadingListStart

\resumeSubheading
{\href{https://hispbd.org/}{\uppercase{HISP Bangladesh Foundation}}}{Administrative Support, Financial Management, Bookkeeping, Report Writing}{Admin and Accounts Officer}{Jan 2022 -- May 2022}
\resumeItemListStart
\resumeItem{Performed assigned tasks in collaboration with teammates}
\resumeItem{Organized/Supported face-to-face and/or virtual team meetings}
\resumeItem{Managed HR Operations including employee documentation, salaries, leaves, promotion, and other related matters}
\resumeItem{Kept track of different projects, and provide reminders to the assigned teams and maintain liaison with the stakeholders}
\resumeItem{Prepared reports, presentations, and financial reports for different projects or research}
\resumeItem{Facilitated the teams with innovative ideas for projects}
\resumeItemListEnd

\resumeSubheading
{\href{https://www.who.int/bangladesh}{\color{blue}\uppercase{World Health Organization (WHO)}}}{Administrative Support, Report Writing}
{Administrative Assistant}{Jan 2020 -- Oct 2021}
\resumeItemListStart
\resumeItem{Drafted and finalized technical reports including program status and the outcome, achievements, goals, and objectives of the project being implemented in Cox’s Bazar for the Forcibly Displaced Myanmar Nationals (FDMNs).}
\resumeItem{Prepared ad-hoc reports on program implementation and the status of any particular issue.}
\resumeItem{Prepared field visit reports, the financial report of the program, and on-demand COVID-19 situation report in the FDMN camps.}
\resumeItem{Provided administrative and secretarial support to provide health interventions to the FDMNs.}
\resumeItem{Drafted SOPs with inputs from stakeholders and joint consultative meetings, MoU with different stakeholders, and proofread various guidelines, books, reports, and other writings; replied to general and administrative correspondence and finalized those.}
\resumeItem{Managed mail, queries, and visitors with tact and discretion.}
\resumeItemListEnd

\resumeSubheading
{\href{https://dghs.gov.bd/}{\uppercase{Directorate General of Health Services (DGHS)}}}{Administrative Support, Bookkeeping, Recruitment, SOP Preparation}{Administrative Assistant}{Nov 2017 -- Nov 2018}
\resumeItemListStart
\resumeItem{Contributed to the development of guidelines on clinical management for the FDMNs prepared by CSC, DGHS, and a book on the development in the health sector of GoB in the last ten years (2009-2018).}
\resumeItem{Participated in the development of different manuals and guidelines.}
\resumeItem{Contributed to the preparation of the epidemiological report of the diphtheria outbreak in the FDMN camps.}
\resumeItem{Provided administrative and secretarial support to provide health interventions to the forcibly displaced population.}
\resumeItem{Provided support for signing MoU and other documents.}
\resumeItemListEnd

\resumeSubHeadingListEnd